---
title: "benchmarkme: Crowd sourced benchmarks"
author: "Colin Gillespie"
date: "2015-12-02"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{benchmarkme: Crowd sourced benchmarks}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r echo=FALSE, purl=FALSE}
library("benchmarkme")
data(sample_results, package="benchmarkme")
res = sample_results
```



## Overview 

A straightforward way of speeding up your analysis, is to buy a better computer. Modern desktops are relatively cheap, especially compared to user time. However, it isn't clear clear if upgrading your computing is worth the cost. `benchmarkme` provides a set of benchmarks to help quantify your system. More importantly, it allows you to compare your timings with other systems.

## Getting Started

To benchmark you system, just run

```{r eval=FALSE, include=TRUE}
library("benchmarkme")
res = benchmark_std(runs = 3)
```

The `runs` account controls the number of replicates. If you have a fast system, then consider increasing this number. Currently, it takes around 3 minutes to run the benchmarks on a standard system.

You can then upload the results using

```{r eval=FALSE}
id = upload_results(res)
```

The object `id` contains a unique identifier that you can use to extract your
dataset in future versions of the package.

## Exploring the Results

Past results are include with the package and can be accessed via

```{r}
data(results, package="benchmarkme")
```

The data set is a simple data frame

```{r}
head(results, 3)
```

and plotted via

```{r, fig.width=7, fig.height=3.5}
plot_past()
```

You can also see how you computer measures up with others

```{r, fig.width=7, fig.height=3.5}
plot(res)
```

## Interactive Tables

If you crave raw numbers, install the `DT` package` 

```{r eval=FALSE}
install.packages("DT")
```

and run 

```{r eval=FALSE}
## Your result is highlighted in orange.
get_datatable(res)
get_datatable_past()
```
