---
title: "Crowd sourced benchmarks"
author: "Colin Gillespie"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Crowd sourced benchmarks}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r echo=FALSE, purl=FALSE}
library("benchmarkme")
data(sample_results, package="benchmarkme")
res = sample_results
```

## Overview 

A straightforward way of speeding up your analysis, is to buy a
better computer. Modern desktops are relatively cheap, especially
compared to user time. However, it isn't clear if upgrading
your computing is worth the cost. The `benchmarkme` package provides a set of
benchmarks to help quantify your system. More importantly, it allows
you to compare your timings with _other_ systems.

## Getting Started

To benchmark your system just run

```{r eval=FALSE, include=TRUE}
library("benchmarkme")
res = benchmark_std(runs = 3)
```

The `runs` argument controls the number of replicates. If you have a fast system, then consider increasing this number. Currently it takes around a minute to run a single benchmark on a standard system (so around $3$ minutes for $3$ runs).

You can upload the results using

```{r eval=FALSE}
id = upload_results(res)
```

The object `id` contains a unique identifier that you can use to extract your
dataset in future versions of the package.

## Exploring the Results

Past results are included in a companion package and can be accessed via

```{r}
data(past_results, package="benchmarkmeData")
```

The data set is a simple data frame

```{r}
head(past_results, 3)
```

and can plotted via

```{r, fig.width=7, fig.height=3.5, message=FALSE}
## shine() # if you have shiny
plot_past()
```

You can also see how you computer measures up with others

```{r, fig.width=7, fig.height=3.5, message=FALSE, results="hide"}
plot(res)
```
The three sets of graphs generated each correspond to a particular set of benchmarks. See the other vignette for details.

There is also a shiny interface that can be accessed via `shine(res)`.

## Interactive Tables

If you crave raw numbers, install the `DT` package` 

```{r eval=FALSE}
install.packages("DT")
```

and run 

```{r eval=FALSE}
## Your result is highlighted in orange.
get_datatable(res)
get_datatable_past()
```

## Input/Output benchmarks

The function `benchmark_std` attempts to assess computational speed. To assess the speed of file access, use

```{r eval=FALSE}
res_io = benchmark_io()
upload_results(res_io)
## Sample size is small, so don't split by byte/blas
plot(res_io, byte_optimize=NULL, blas_optimize=NULL)
```

This benchmark creates a $5$, $50$ and $200$ MB data frame and times reading/wrting of the file. By default the files 
are created in a temporary directory specified as
```{r eval=FALSE}
Sys.getenv("TMPDIR")
```
Depending on your set-up, this can be on a network drive. You can change where the files are created via

```{r eval=FALSE}
res_io = benchmark_io(tmpdir="some_other_directory")
```






